\subsection{Q1d}

The code and output are already shown in the previous subsections, but I'll discuss them here.
To assess the goodness-of-fit, we perform a G-test on our binned models. The number of degrees of freedom is given by $k = n - c$, 
where $n = N_{\rm bins}$ is the number of data points and $c = 4$ is the number of constraints. The number of data points is equal
to the number of bins and the constraints are given by the free parameters (3) and the normalization of the histogram (1).

The G-test statistic is given by
\begin{equation}
    G = 2 * \sum_{i = 0}^{N_{\rm bins} - 1} O_{i} \ln\left( \frac{O_{i}}{E_{i}} \right) \, ,
\end{equation}
where $O_{i}$ is the number of observed counts in bin $i$ (integers) and $E_{i}$ is the expected number of counts in this bin. 
In empty bins, we have $G = 0$, so those can be omitted in this calculation. Note that the G-test requires the observed histogram
and the model to integrate to the same value, i.e., the number of observations. However, my Romberg integration method is not accurate
enough (even with $m = 10$) to get this normalization to a point where the G-test gives believable results for all datasets. Therefore,
we provide the G-test results using both the model as is and the model that is renormalized to integrate exactly to the number of data points.

The p-values (or significances $Q$) of our models are calculated using $Q = 1 - P(x, k)$, where $P(x, k)$ is the CDF of the chi-squared distribution,
evaluated at $x = G$ with $k = N_{\rm bins} - 4$ degrees of freedom. The CDF of the chi-squared distribution is given by
\begin{equation}
    P(x, k) = \frac{\gamma \left( \frac{k}{2}, {x}{2} \right)}{\Gamma \left( \frac{k}{2} \right)} \,
\end{equation}
where $\Gamma$ is the gamma function and $\gamma$ is the lower incomplete gamma function.

Comparing our G-test results using the renormalized models, the p-values of the Poisson models are always higher, indicating that these models are better fits. 
This is expected, since the data is generated from a Poisson process, so our model should be Poissonian and not Gaussian, as assumed by the chi-squared fit.
